`flippant` -- An `R` package for the automated  analysis of dithionite

### 2015-09-16 inst/manuscript/manuscript.rmd
Provide funding info (Anant will have to check);

#Funding
J.G., R.J.C. and the Proteomics Core at WCMC-Q were supported by ``Biomedical 
#Acknowledgements

>>>>

#Funding
J.G., R.J.C. and the Proteomics Core at WCMC-Q were supported by ``Biomedical 
Research Program'' funds at Weill Cornell Medical College in Qatar, a program 
funded by Qatar Foundation. B.P. was supported by a grant from Qatar National 
Research Fund’s National Priority Research Program (5-669-1-112) to J.G. and
A.K.M.

#Acknowledgements
